---
output:
 pdf_document:
   includes:
     in_header: header_multi.tex
geometry: margin=0.5cm
params:
 year: 2019
header-includes: 
- \usepackage{booktabs}
- \usepackage{sectsty} \sectionfont{\centering}
- \usepackage{titling}
- \pretitle{\begin{center}
    \includegraphics[width=6.5in,height=5in]{"C:/Users/Chido/Pictures/logo.jpg"}\LARGE\\}
- \posttitle{\end{center}}

---



---
title: "Death information for `r params$year`, MRC/WITS-AGINCOURT"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RODBC)
library(kableExtra)
library(RColorBrewer)
library(ggrepel)
library(waffle)


```

# Cause of Death
```{r, echo = FALSE}

myPalette <- brewer.pal(6, "Set2") 

con <- odbcConnect("SummaryIndicators")
 cod_ab <- sqlQuery(con,"SELECT distinct Years,Ordered,AgeGroup, Total
  FROM CFB..CoDVA 
  ") %>%
   filter(Years == params$year)
  
  cod_ad <- sqlQuery(con,"SELECT Years, AgeGroup, Total, substring(Cause,patindex('%[A-Z]%', Cause), len(Cause) +1) as Cause, Rnk, CntAll
  FROM CFB..CoDVA 
  order by Years,Ordered") %>%
   filter(Years == params$year) %>%
    select(AgeGroup, Total, Cause, Rnk, CntAll) %>%
    rename( 'Age Group'=AgeGroup, 'Cause of Death' = Cause, Rank = Rnk, Number = CntAll)
  
  cod_ae <- sqlQuery(con,"SELECT *
  FROM CFB..VA_CoDp 
  order by Years") %>%
   filter(Years == params$year) %>%
    select(DiedAt, Under5, 'Age5-14','Age15-49','Age50-64','65AndOlder', TOTALDEATH) %>%
    arrange(DiedAt)    %>%
    rename('Place of Death'= DiedAt, 'Under 5' = 'Under5', 'Aged 5-14'='Age5-14','Aged 15-49'='Age15-49','Aged 50-64'= 'Age50-64','Aged 65 and older'='65AndOlder', 'Total deaths' = TOTALDEATH ) 
  
  cod_af <- sqlQuery(con,"SELECT *
  FROM CFB..VA_CoDp 
  order by Years") %>%
   filter(Years == params$year) %>%
    select(DiedAt, TOTALDEATH) %>%
    mutate(prop = TOTALDEATH/sum(TOTALDEATH)) %>%
    arrange(prop) %>%
    mutate(ymax = cumsum(prop))
   
  cod_af$ymin <- c(0, head(cod_af$ymax, n=-1))
  
# Compute label position
cod_af$labelPosition <- (cod_af$ymax + cod_af$ymin) / 2

# Compute a good label
cod_af$label <- paste0(cod_af$DiedAt, "\n Deaths: ", cod_af$TOTALDEATH)
 
```

\btwocol


```{r, echo = FALSE, out.height = "120%"}
ggplot(cod_ab, aes(x=Ordered, y =Total)) +
  geom_bar(stat = "identity", fill="yellow4")+
#  geom_text(aes(label=len), vjust=1.6, color="white", size=3.5)+
  geom_text(aes(label = Total), vjust=1.6, color="white", size=5)+
 scale_x_discrete(limits = c("Neonates","<1","1-4", "5-19","20-49","50-64","65+")) +
  labs(x = 'Age Group', y = 'Number of people dying', title ='Number of deaths per age group')+
                     theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```







\begingroup
\fontsize{25}{25}\selectfont
\textcolor{olive}{`r sqlQuery(con,"SELECT Years, AgeGroup, Total, substring(Cause,patindex('%[A-Z]%', Cause), len(Cause) +1) as Cause, Rnk, CntAll FROM CFB..CoDVA order by Years,Ordered") %>%filter(Years == 2019,  Rnk ==1) %>% filter( Total == max(Total)) %>% select(Cause)`} 
are the major cause of death among adults aged
\textcolor{olive}{`r sqlQuery(con,"SELECT Years, AgeGroup, Total, substring(Cause,patindex('%[A-Z]%', Cause), len(Cause) +1) as Cause, Rnk, CntAll FROM CFB..CoDVA order by Years,Ordered") %>%filter(Years == 2019,  Rnk ==1) %>% filter( Total == max(Total)) %>% select(AgeGroup)`} 
in MRC/Wits-Agincourt HDSS Area in `r params$year`. They account for 
 \begingroup
\fontfamily{ppl}\fontsize{50}{50}\selectfont
 \textbf{\textcolor{olive}{`r sqlQuery(con,"SELECT Years, AgeGroup, Total, Cause, Rnk, CntAll FROM CFB..CoDVA order by Years,Ordered") %>% filter(Years == 2019,  Rnk ==1) %>% filter( Total == max(Total)) %>% mutate(perc = floor(CntAll/Total* 100))%>% select (perc)`\%}} 
 \fontsize{25}{25}\selectfont
 \endgroup
 of all the deaths in this age group
\endgroup

\etwocol


```{r pressure, echo=FALSE}
kable(cod_ad,booktabs = T)%>%
kable_styling(latex_options = "striped", stripe_index = c(1,7:11,17:21), position = "center")

```



# Place of death

```{r, echo=FALSE}
kable(cod_ae,booktabs = T) %>%
  kable_styling( position = "center")

```

# ```{r, echo=FALSE }
# 
# 
# 
# # Make the plot
# ggplot(cod_af, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=DiedAt)) +
#   geom_rect() +
#    geom_label_repel( x=3.5, aes(y=labelPosition, label=label), size=3) +
#  # geom_text_repel( x=2, aes(y=labelPosition, label=label, color=DiedAt), size=4, ) + # x here controls label position (inner / outer)
#   scale_fill_brewer(palette=3) +
#   scale_color_brewer(palette=3) +
#   coord_polar(theta="y") +
#   xlim(c(2, 4)) +
#   theme_void() +
#   theme(legend.position = "none")
# ```

```{r, echo=FALSE }

cod_afg <- sqlQuery(con,"SELECT *
  FROM CFB..VA_CoDp 
  order by Years") %>%
  filter(Years == 2019) %>%
  select(DiedAt, TOTALDEATH) %>%
  mutate(prop = TOTALDEATH/sum(TOTALDEATH)*100) %>%
  mutate(prop = round(prop, 0)) %>%
  arrange(desc(prop))

cases_afg <- cod_afg$prop
names(cases_afg) <- cod_afg$DiedAt

waffle(cases_afg)



```